\pkg{cubble}: An \proglang{R} Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2023-06-29 cubble.Rmd
Changes section 2.3

Table \@ref(tab:funs) summarises the functions implemented in the \pkg{cubble} package and Table \@ref(tab:methods) details the methods implemented for each of the three cubble classes. The \code{cubble_df} class handles methods that behave consistently in both spatial and temporal cubble. When the method has distinct behavior, it is implemented separately in \code{spatial_cubble_df} and \code{temporal_cubble_df}.

@@

The pair of cubble verbs, \code{face_temporal()} and \code{face_spatial()}, pivots the cubble object between its two forms, as illustrated in Figure \ref{fig:face}. The code below connects the a spatial cubble (\code{cb_nested}) and a temporal temporal (\code{cb_long}) introduced in Section \@ref(object) with \code{face_temporal()} and \code{face_spatial()}:

>>>>

The \pkg{cubble} package has several functions implemented for data wrangling and to facilitate data analysis as summarized in Table \@ref(tab:funs). In addition, for each of the three cubble classes there are number of methods implemented that facilitates the handling of the data as shown in Table \@ref(tab:methods). In particular, the \code{cubble_df} class handles methods that behave consistently in both spatial and temporal cubble. When the method has a distinct behavior on the spatial and temporal cubble, it is implemented separately in \code{spatial_cubble_df} and \code{temporal_cubble_df}.

@@

The pair of cubble verbs, \code{face_temporal()} and \code{face_spatial()}, pivots the cubble object between its two forms or faces, as illustrated in Figure \ref{fig:face}. The code below connects a spatial cubble (\code{cb_nested}) and a temporal cubble (\code{cb_long}), introduced in Section \@ref(object), with \code{face_temporal()} and \code{face_spatial()}:

### 2023-06-29 cubble.tex
Changes section 2.3

Table \ref{tab:funs} summarises the functions implemented in the \pkg{cubble} package and Table \ref{tab:methods} details the methods implemented for each of the three cubble classes. The \code{cubble_df} class handles methods that behave consistently in both spatial and temporal cubble. When the method has distinct behavior, it is implemented separately in \code{spatial_cubble_df} and \code{temporal_cubble_df}.

@@

The pair of cubble verbs, \code{face_temporal()} and \code{face_spatial()}, pivots the cubble object between its two forms, as illustrated in Figure \ref{fig:face}. The code below connects the a spatial cubble (\code{cb_nested}) and a temporal temporal (\code{cb_long}) introduced in Section \ref{object} with \code{face_temporal()} and \code{face_spatial()}:

>>>>

The \pkg{cubble} package has several functions implemented for data wrangling and to facilitate data analysis as summarized in Table \ref{tab:funs}. In addition, for each of the three cubble classes there are number of methods implemented that facilitates the handling of the data as shown in Table \ref{tab:methods}. In particular, the \code{cubble_df} class handles methods that behave consistently in both spatial and temporal cubble. When the method has a distinct behavior on the spatial and temporal cubble, it is implemented separately in \code{spatial_cubble_df} and \code{temporal_cubble_df}.

@@

The pair of cubble verbs, \code{face_temporal()} and \code{face_spatial()}, pivots the cubble object between its two forms or faces, as illustrated in Figure \ref{fig:face}. The code below connects a spatial cubble (\code{cb_nested}) and a temporal cubble (\code{cb_long}), introduced in Section \ref{object}, with \code{face_temporal()} and \code{face_spatial()}:
